Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2017-07-05 workflow/workflow.Rmd
add sandrines comment on nested batch-bio

After sample filtering, we are left with `r ncol(se)` [SD: Check.] good quality cells.

@@

@@

Note that there is partial nesting of batches within clusters (i.e., cell type), which could be problematic when correcting for batch effects in the dimensionality reduction step below. [SD: Might refer to this issue below again.]

@@

The principal component analysis (PCA) of the normalized values shows that, as expected, cells do not cluster by batch but by the original clusters (Figure \@ref(fig:pcanorm)). Overall, it seems that normalization was effective at removing batch effects. [SD: Maybe here: " without removing biological signal, in spite of the partial nesting of batches within clusters".]

>>>>

After sample filtering, we are left with `r ncol(se)` good quality cells.

@@

[FP: add an additional comment to justify that we keep only 1000 most variable genes. We can say that it is enough to recover the signal from [@Fletcher2017]. ]

@@

Note that there is partial nesting of batches within clusters (i.e., cell type), which could be problematic when correcting for batch effects in the dimensionality reduction step below.

@@

The principal component analysis (PCA) of the normalized values shows that, as expected, cells do not cluster by batch but by the original clusters (Figure \@ref(fig:pcanorm)). Overall, it seems that normalization was effective at removing batch effects without removing biological signal, in spite of the partial nesting of batches within clusters.
